\textbf{Parallel dragonfly algorithm} \\[2ex] \large High Performance Computing for Data Science course 2024/2025

### 2025-08-30 text-paper/paper.tex
put matricola IDs

\title{\textbf{Parallel dragonfly algorithm} %
  \\[2ex] \large High Performance Computing for Data Science course 2024/2025}

\author[1]{Mattia Santaniello}
\author[2]{Alessio Zeni}
\affil{University of Trento}

@@

\end{multicols}
\section{Final execution and results}
To sum up, the presented code is highly flexible and scalable, and it could be used for small optimizations on low-end systems as well as training other methods in an HPC architecture.
The code is available on GitHub, and it can be freely used in different applications.

>>>>

\title{\textbf{Parallel dragonfly algorithm} %
  \\[2ex] \large High Performance Computing for Data Science course 2024/2025
}

\author{
  Mattia Santaniello \quad  mat. 258777 \\ Alessio Zeni  \quad
  mat. 256130  
}

@@

\end{multicols}
\section{Final execution and results}
To sum up, the presented code is highly flexible and scalable, and it could be used for small optimizations on low-end systems as well as training other methods in an HPC architecture.
The code is available on GitHub, and it can be freely used in different applications.\cite{GitHub}
